A Loop Quantum Gravity Inspired Action for the Bosonic String and Emergent Dimensions at Large Scales

### 2025-08-25 AoP/response-to-referee-r2.tex

\documentclass{article}
\usepackage[square,comma]{natbib}
\def\lettertitle{Author Response to Reviews of}
\def\papertitle{A Loop Quantum Gravity Inspired Action for the Bosonic String and Emergent Dimensions at Large Scales}
\def\authors{Deepak Vaid and Lin Teixeira de Sousa}
\def\journal{Annals of Physics}
\def\doi{AOP 81029}
\def\date{\today}

\input{AR_to_RC.tex}

\date{}

We thank the editor for his patience through the whole process and the referee for taking the time to review the revised manuscript.

\section{Reviewer \#1}

\subsection{Clarifications and Enhancements}

\RC The discussion on the duality between $h_{ab}$ and $h^{ab}$ (Section 2) is now clearer, but a brief mention of how this duality might manifest in observable string dynamics (e.g., through measurable spectra or scattering amplitudes) would provide an wider physical interpretation.

\AR We have added the following paragraph right after ``\emph{and the string tension inversion is reminiscent of S-duality’s strong-weak coupling correspondence.}'' to explain this point:

\emph{Physically, one way in which this duality could manifest in the real world is in the mass spectrum of string excitations which when computed in the strong-coupling regime should exhibit a precise correspondence with spectra in the weak-coupling limit under the transformation rules (2.7a)-(2.7c), while world-sheet correlation functions should satisfy similar duality relations, potentially providing calculable predictions for string phenomenology at both energy scales.}

\RC The connection to the Kalb-Ramond field (Section 3.2) is well-justified, but a brief comment on whether this implies any constraints on the Kalb-Ramond field's dynamics (e.g., torsionless backgrounds) would be insightful.

\AR We have added the following para at the end of Sec 4A, right after ``\emph{since the co- efficient in eq (4.16) is a true scalar and the Levi-Civita symbol is itself a density.}''

\emph{This pullback relationship would suggest a restriction on the allowed bulk configurations. Since the worldsheet area spectrum is discrete due to the underlying LQG quantization, the Kalb-Ramond field strength must be correspondingly quantized. This is analogous to flux quantization in the quantum Hall effect, where the magnetic flux through the 2D electron system is constrained to be integer multiples of $h/e$. In our case, the integrated field strength $\int H_{\mu \nu \rho}$ over appropriate 3-cycles in the bulk should be quantized in units related to the fundamental area quantum $\Delta$, restricting the allowed background field configurations to those compatible with the discrete worldsheet area spectrum.}

\subsection{Open Questions and Future Directions (Section 8.C)}

\RC Open Questions and Future Directions (Section 8.C):
The discussion on emergent dimensions and their cosmological implications (Section 6) is somewhat speculative. A brief acknowledgment of the phenomenological challenges (e.g., observational constraints on extra dimensions) would provide more support.

\AR

\RC The suggestion of a (2+1)-dimensional fundamental spacetime (Section 6) requires more evidence or references to support this claim. You might provide references to recent work on lower-dimensional gravity or holography that could bolster this argument.

\AR

\subsection{Technical Details}

\RC The derivation of the relation between $\Delta_{ab}$ and the Kalb-Ramond field (Eq. 3.21) is now clearer, but a step-by-step derivation in an appendix or supplementary material would provide reproducibility.

\AR

\subsection{Cosmological Implications (Section 7)}

\RC The interpretation of the emergent dimension $X^r$ as a "scaling dimension" is compelling. However, the link to the cosmological horizon scale (Page 30) is tentative. A brief discussion of how this might align or conflict with current cosmological data would be valuable.

\AR

\bibliographystyle{apalike}

\bibliography{../lqg-strings.bib}

\end{document}

### 2025-08-25 lqg-strings.tex
T4: AOP final revisions task - completed Section 2 duality clarification, identified remaining 4 reviewer requirements

% Biblatex setup
% The default is the 'numerical' style.
%\usepackage[backend=biber,url=true,eprint=true,doi=true,sorting=none,backref=true,style=phys]{biblatex}
% We use the following bibliography databases:
%\usepackage{bibtex}
%\addbibresource{../bib_library.bib}
% End biblatex

@@

%text
\newcommand{\ie}{\textit{i.e.}~}
\newcommand{\eg}{\textit{e.g.}~}
\newcommand{\wrt}{\textit{w.r.t.}~}
\newcommand{\etc}{\textit{etc.}~}

@@

\title{A Loop Quantm Gravity Inspired Action for the Bosonic String and Emergent Dimensions at Large Scales}

\author{Deepak Vaid}
\email{dvaid79@gmail.com}
\affiliation{}
\author{Luigi Teixeira de Sousa}
\email{luigi.tiraque@gmail.com}
\affiliation{Universidade Federal de São Carlos, Brasil}

@@

The second approach is called \emph{loop quantum gravity} or ``LQG'' for short \cite{Rovelli1998Loop,Rovelli2015Covariant}. LQG is ostensibly meant to be a theory of ``pure quantum gravity'', that is gravity without any matter. Matter can always be ``added'' in by hand into the framework but is not present to begin with. LQG is also built upon a rigorous mathematical framework which applies the well-established Dirac procedure of quantization to canonical (ADM) Einstein gravity, and this is crucial, written in terms of Ashtekar variables which is a connection based approach as opposed to the conventional metric formalism. LQG has concrete predictions such as discreteness of physical areas \cite{Rovelli1993Area,Rovelli1994Discreteness}, and also has rigorous mathematical results which reproduce the black hole entropy formulae for Einstein gravity \cite{Rovelli1996Black}. Moreoever it allows us to construct a non-perturbative framework for quantum geometry which makes it possible to probe regimes which do not appear to be accessible via string theory.

@@

The following is the outline of the paper along with a brief summary of what is accomplished in each section. For those seeking a rapid review of the principle areas of diffence between the two theories \autoref{sec:history} provides a bird's eye view of research spanning a period of nearly sixty years.

Those already familiar with the essentials of LQG (primarily area quantization) and the question of background independence of string theory can skip ahead to \autoref{sec:modified-ng} where we being by recalling the Nambu-Goto action and suggest a simple modification which incorporates our \textbf{central dogma}, which is that \emph{there must exist a smallest possible area $\Delta$ which is physically measurable.}\footnote{In recent work \cite{Borissova2024From} a very similar expression to ours for the modified Nambu-Goto action has been arrived at by considering a version of LQG called ``area metric gravity''.}

@@

We show that this action can be expanded in terms of a small coupling constant $k = l_{pl} / l_s$ where the Planck length - the length at which quantum geometric effects become important - $l_{pl}$ is much smaller than the string scale $l_s$ and therefore $k \ll 1$. We point out that the lowest order correction to the NG action can be interpreted in the context of bimetric gravity. In \autoref{sec:bimetric-string} we expand upon this observation and suggest a new action for the ``bimetric string'', along the lines of bimetric gravity. We find both, the Nambu-Goto and the Polaykov forms of this action. Furthermore, we show that the phenomenological correction $\Delta$ introduced earlier is related to the pullback of the Kalb-Ramond field $B_{\mu \nu}$ into the worldsheet.

@@

There are various appendices containing details of calculations and background information. In Appendix \ref{sec:modified-eom} we derive the equations of motion for the modified Nambu-Goto action. Appendix \ref{sec:polyakov-ng-relation} shows how the equations of motion extracted from the Nambu-Goto and Polakov versions of the modified string action are equivalent to each other.

@@

In the decades prior to the advent of string theory a great deal of effort was put into attempting to quantize gravity via both the Lagrangian and Hamiltonian approaches. The Hamiltonian approach involves, as stated earlier, a choice of the foliation of the background geometry into a collection of spacelike surfaces $\Sigma_t$. Central to this approach was the ADM (Arnowitt-Deser-Misner) formalism which allows one to construct a Hamiltonian $H_{GR}$ for general relativity starting from the Einstein-Hilbert action $S_{EH}$. The resulting phase space is coordinatized by a configuration variable which is the 3-metric $h_{ab}$ of the ``leaves'' $\Sigma_t$ of the foliation and a momentum variable which is a function of the extrinsic curvature $k_{ab}$ of the leaves\footnote{Our notational convention is the following. Lowercase Greek letters from the middle of the alphabet $\mu, \nu, \ldots$ are spacetime indices which run from $(0 \ldots 3)$, whereas lowercase Roman letters $a,b,\ldots$ are spatial indices for quantities which live solely on the surfaces $\Sigma_t$ and take values in $(1,2,3)$}. The gravity Hamiltonian turns out to be a sum of two constraints known as the diffeomorphism (or ``momentum'') constraint $H_{diff}$ and the Hamiltonian constraint $H_{ham}$:
\begin{equation}
	H_{GR} = H_{diff} + H_{ham},
\end{equation}
and these are, in turn, functionals on the phase space of general relativity written in terms of $h_{ab}$ and $k_{ab}$. The idea then is that physical states of the theory $\ket{\Psi_{phys}} $, which can be written as functionals $\Psi[h_{ab}]$ of the 3-metric $h_{ab}$ , must be annihilated by these constraints:
\begin{equation}
	H_{GR} \ket{\Psi_{phys}} \equiv 0
\end{equation}
While this procedure is straightforward in principle, in practice it was impossible to implement in the quantum theory due to the highly complicated non-polynomial dependence of the diffeomorphism and Hamiltonian constraints on the configuration and momentum variables. This unfortunate state of affairs persisted until the late 1980s when Abhay Ashtekar \cite{Ashketar1986New,Ashtekar1987New} recast general relativity as a BF theory of a dualised $\mathfrak{sl} (2 , \C)$ connection (which becomes the self-dual part of said connection in the case of $\beta = i$)
\begin{equation} \label{eqn:self-dual-spin-connection}
	A_{\mu} ^{I J} = \omega ^{I J} _{\mu} - \frac{\beta}{2} \varepsilon ^{I J} _{\ \ K L} \omega ^{K L} _{\mu}
\end{equation}
and its conjugate momenta
\begin{equation} \label{eqn:densitized-tetrad}
	B^{I J} _{\mu \nu} = \left( \delta ^{I} _{K} \delta ^{J} _{L} + \frac{1}{2 \beta} \varepsilon ^{I J} _{\ \ K L} \right) e^{K} _{[ \mu} e^{L} _{\nu ]} ,
\end{equation}
which when restricted to a 3-dimensional hypersurface where $* (e \wedge e) = 0$ reduces to
\begin{equation} \label{eqn:Ashtekar-connection-canonical}
	A^{i} _{a} = \omega ^{i} _{a} + \beta K^{i} _{a}
\end{equation}
\begin{equation} \label{eqn:Ashtekar-E-field-canonical}
	E^{a} _{i} = \sqrt{q} e^{a} _{i} = \frac{1}{2} \varepsilon ^{a b c} \varepsilon _{i j k} e^{j} _{b} e^{k} _{c} ,
\end{equation}
with $K^{i} _{a}$ being the triad version of the extrinsic curvature $K_{a b} = \frac{1}{2} \mathcal{L}_{n} q_{a b}$ and $q$ the 3-metric. Ashtekar realized that the constraints of general relativity, when expressed in terms of these ``new variables'', simplified drastically and became polynomial functions of the tetrad and connection variables. It was quickly realized by various researchers that the resulting theory could be quantized using the same methods used to quantize Yang-Mills gauge theory \cite{Ashtekar1992Weaving,Ashtekar2004Background} and that the diffeomorphism constraint could be solved exactly in terms of so-called \emph{spin-network} states \cite{Rovelli1988Knot,Rovelli1990Loop,Ashtekar1992Gravitons}.

Following this, work by Rovelli and Smolin \cite{Rovelli1993Area,Rovelli1994Discreteness} demonstrated a remarkable feature of this theory, which came to be known as ``Loop Quantum Gravity'', was that one could construct quantum operators for geometric quantities such as areas of two-dimensional surfaces and volumes of three-dimensional regions. Moreover, these operators could be diagonalized exactly in the spin-network basis and a discrete spectrum for quantum of area and quantum of volume could be derived. This was the first time that physicists had discovered the ``atoms of space'' or the ``quanta of geometry'' in the true sense of the expression, in a theory of quantum gravity. One of the early triumphs of this formalism, which has unfortunately not received enough attention over the years by the larger high energy theory community, was the calculation of the entropy of a Schwarzschild black hole \cite{Rovelli1996Black} in a fully quantum mechanical framework and showing that it matched the expected expression $S \sim A/4$ for the Bekenstein-Hawking entropy.

One key feature of the discreteness of spacetime itself is that the Ashtekar connection $A^{i} _{a}$ \footnote{Here, the index convention followed is that lowercase $i , j , k$ refer to 3-dimensional flat internal ($\mf{su}(2)$) indices and lowercase $a , b , c$ refer to 3-dimensional curved spacetime indices} can no longer be a continuous function of spacetime, rather it becomes a \emph{distribution}, assuming a constant value on one patch of space, then another value at another patch, etc \cite{Bodendorfer-LQG,Rovelli2015Covariant}. The consequence of this non-continuous distributional nature of the connection is that the triad (or Ashtekar electric field) operator, which formally would be
\begin{equation} \label{eqn:triad-operator}
	\Hat{\widetilde{E}}{}^{a} _{i} = - 8 \pi i \hbar G \frac{\delta}{\delta A^{i} _{a}}
\end{equation}
becomes ill-defined since $A^{i} _{a}$ is non-continuous (in particular, at the edges of a polyhedra it changes abruptly), so the triad needs to be \emph{smeared} over a surface where $A^{i} _{a}$ is constant
\begin{equation} \label{eqn:triad-flux-operator}
	\Hat{E}_{i} (S) = - 8 \pi i \hbar G \int _{S} \diff S_{a}  \frac{\delta}{\delta A^{i} _{a}} ,
\end{equation}
where $\diff S_{a} = \diff \sigma ^{b} \wedge \diff \sigma ^{c} \varepsilon _{a b c}$. This naturally leads to the \emph{area operator} of said surface
\begin{equation} \label{eqn:area-operator}
	\Hat{A} (S) = - 8 \pi i l_{pl} ^2 \beta \int _{S} \sqrt{\diff S_{a} \diff S_{b} \frac{\delta}{\delta A^{i} _{a}} \frac{\delta}{\delta A_{b i}}} .
\end{equation}
Notably, since $A^{i} _{a}$ is a $\mf{su}(2)$-valued connection, in the basis which diagonalises the area operator (the \emph{spin network} basis \cite{Bodendorfer-LQG}) $\ket{\Tr (h^{(j)} _{c} (A))}$, the eigenvalues of the area operator are just proportional to \emph{angular momentum} eigenvalues
\begin{equation} \label{eqn:area-eigenvalues}
	\Hat{A} \ket{\Tr (h^{(j)} _{c} (A))} = 8 \pi l_{pl} ^2 \beta \sqrt{j (j + 1)} \ket{\Tr (h^{(j)} _{c} (A))} ,
\end{equation}
with $j$ being the representation label of $\mf{su}(2)$ along the spin network edge piercing the surface under consideration. Thus, spin network edges carry angular momenta.

@@

Here, $k = l_{pl} / l_s$, where $l_{pl}$ is the Planck scale, the scale at which quantum geometric effects become important; $l_s$ is the string scale where quantum geometric effects due to area quantization become small; for the time being we take $\Delta$ to be a scalar constant which corresponds to the minimum quantum of area at the Planck scale\footnote{We will see later that $\Delta$ is, in fact, a scalar density of weight 2 which can be taken to be the determinant of an antisymmetric worldsheet tensor $\Delta _{a b} (x)$ and corresponds to the square of the quantum of area at the point $x$ where the edges of the bulk spin network state pierce the WS and endow it with quanta of area as described in the previous section.}. In the limit that $l_s \gg l_{pl}$, $k \ll 1$ and the string action reduces to the conventional Nambu-Goto action with small corrections coming from quantum geometry. In this limit we can expand the integrand as follows:
\begin{equation} \label{eqn:inverse-metric-correction}
	\sqrt{- (h + k \Delta)} \sim \sqrt{- h}\left(1 - \frac{1}{2} \frac{k \Delta}{(- h)} + \mc{O}(k^2/h^2)\right).
\end{equation}

If we take $k$ to be an expansion parameter, then it follows that it should also be small. The physical justification for this is the following picture. The microscopic picture of geometry at the Planck scale, which we adopt as the ``correct'' picture, is that given by loop quantum gravity in terms of spin networks and spin foams. The worldsheet picture emerges when one considers a large enough section of the spin network with a sufficiently large number of punctures. In this limit, the spin network can be approximated by a smooth geometry, and the worldsheet picture emerges as a low-energy effective description of the spin network. When $k \sim 1$, the discrete structure of the underlying spin network becomes manifest and the smooth worldsheet approximation is no longer valid, indicating that a full quantum gravitational treatment - i.e. where geometry itself is fully quantum - is required.

@@

The action eq \eqref{eqn:modified-ng-action} has manifest background Poincaré invariance since just like the regular Nambu-Goto action since all its terms are derivatives of $X^{\mu}$ with all Lorentz indices contracted, thus are Lorentz scalars. At first glance it might seem to not be WS reparameterization invariant because of the second term, however, this is corrected by the fact that $\Delta$ is a scalar \emph{density} of weight 2, thus counteracting the inverse metric determinant. Moreover, if we look at that expression we see that it can be written as:
\begin{equation} \label{eqn:modified-ng-action-v2}
	S'_{NG}[h_{ab}] = -T \int \diff ^2 x \left( \sqrt{- h} - \frac{1}{2} {k \Delta}{\sqrt{- (h^{-1})}} \right),
\end{equation}
where $h^{-1}$ is now the determinant of the \emph{inverse} metric $h^{ab}$. As such, in the expression \eqref{eqn:modified-ng-action} we can see a duality between the first and second terms. If we replace the metric $h_{ab}$ by its inverse $h'_{ab} \equiv h^{ab}$, then the action in terms of $h'_{ab}$ is the same as \eqref{eqn:modified-ng-action}, but with the difference that the factor of $k \Delta / 2$ is mapped to $2 / (k \Delta)$:
\begin{align} \label{eqn:modified-ng-action-v3}
	S'_{NG}[h'_{ab}] & = -T' \int \diff ^2 x' \left( \sqrt{- h'} - \frac{2}{k \Delta} \sqrt{- (h')^{-1}} \right) \nonumber \\
	                 & = -T' \int \diff ^2 x' \left( \sqrt{- h'} - \onehalf {k' \Delta'}\sqrt{- (h')^{-1}} \right),
\end{align}
which has the same form as the original action \eqref{eqn:modified-ng-action}, as long as we make the replacements
\begin{subequations}
	\begin{equation} \label{eqn:T'}
		T \rightarrow T' = - \frac{1}{2} k T
	\end{equation}
	\begin{equation} \label{eqn:k-Delta}
		\frac{1}{2} {k \Delta} \rarrow \frac{1}{2} {k' \Delta'} = \frac{2} {k \Delta}
	\end{equation}
	\begin{equation} \label{eqn:d2x}
		\diff ^2 x \rightarrow \diff ^2 x' = \Delta \diff ^2 x
	\end{equation}
\end{subequations}
(or equivalently $\diff x^{a} \rightarrow \diff x' _{a} = \Delta _{a b} \diff x^{b}$). This is a duality between the physics at the Planck scale and the physics at the string scale, \ie between strong coupling ($k' \gg 1$) and weak coupling ($k \ll 1$), small worldsheet areas $h_{ab}$ and large worldsheet areas $h'_{ab}$ and between large string tension $T$ and small string tension $T'$.

This duality is reminiscent of, but also distinct from, the T and S dualities in string theory. In T-duality the behavior of a string compactified on a circle of radius $R$ is related to the behavior of a string compactified on a circle of radius $\alpha'/R$. In S-duality the physics at strong string coupling $g_s \gg 1$ can be mapped to the physics at weak string coupling $g_s \ll 1$. In our case, the duality is between a description of physics at large string tension $T$ and small worldsheet areas $h_{ab}$ and a description of physics at small string tension $T'$ and large worldsheet areas $h'_{ab} = (h_{ab})^{-1}$. This appears to have features of both T-duality and S-duality, in that the area inversion is reminiscent of T-duality and the string tension inversion is reminiscent of S-duality's strong-weak coupling correspondence.

>>>>

@@

%text
\newcommand{\ie}{\textit{i.e.}}
\newcommand{\eg}{\textit{e.g.}}
\newcommand{\wrt}{\textit{w.r.t.}}
\newcommand{\etc}{\textit{etc.}}

@@

\title{A Loop Quantum Gravity Inspired Action for the Bosonic String and Emergent Dimensions at Large Scales}

\author{Deepak Vaid}
\email{dvaid79@gmail.com}
\affiliation{502, Broadway Apartments, Mangaluru, Karnataka, India}
\author{Lin Teixeira de Sousa}
\email{luigi.tiraque@gmail.com}
\affiliation{Universidade Federal de São Carlos, Brasil}

@@

The second approach is called \emph{loop quantum gravity} or ``LQG'' for short \cite{Rovelli1998Loop,Rovelli2015Covariant}. LQG is ostensibly meant to be a theory of ``pure quantum gravity'', that is gravity without any matter. Matter can always be ``added'' in by hand into the framework but is not present to begin with. LQG is also built upon a rigorous mathematical framework which applies the well-established Dirac procedure of quantization to canonical (ADM) Einstein gravity, and this is crucial, written in terms of Ashtekar variables which is a connection based approach as opposed to the conventional metric formalism. LQG has concrete predictions such as discreteness of physical areas \cite{Rovelli1993Area,Rovelli1994Discreteness}, and also has rigorous mathematical results which reproduce the black hole entropy formulae for Einstein gravity \cite{Rovelli1996Black}. Moreover it allows us to construct a non-perturbative framework for quantum geometry which makes it possible to probe regimes which do not appear to be accessible via string theory.

@@

The following is the outline of the paper along with a brief summary of what is accomplished in each section. For those seeking a rapid review of the principle areas of difference between the two theories \autoref{sec:history} provides a bird's eye view of research spanning a period of nearly sixty years.

Those already familiar with the essentials of LQG (primarily area quantization) and the question of background independence of string theory can skip ahead to \autoref{sec:modified-ng} where we begin by recalling the Nambu-Goto action and suggest a simple modification which incorporates our \textbf{central dogma}, which is that \emph{there must exist a smallest possible area $\Delta$ which is physically measurable.}\footnote{In recent work \cite{Borissova2024From} a very similar expression to ours for the modified Nambu-Goto action has been arrived at by considering a version of LQG called ``area metric gravity''.}

@@

We show that this action can be expanded in terms of a small coupling constant $k = l_{pl} / l_s$ where the Planck length - the length at which quantum geometric effects become important - $l_{pl}$ is much smaller than the string scale $l_s$ and therefore $k \ll 1$. We point out that the lowest order correction to the NG action can be interpreted in the context of bimetric gravity. In \autoref{sec:bimetric-string} we expand upon this observation and suggest a new action for the ``bimetric string'', along the lines of bimetric gravity. We find both, the Nambu-Goto and the Polyakov forms of this action. Furthermore, we show that the phenomenological correction $\Delta$ introduced earlier is related to the pullback of the Kalb-Ramond field $B_{\mu \nu}$ into the worldsheet.

@@

There are various appendices containing details of calculations and background information. In Appendix \ref{sec:modified-eom} we derive the equations of motion for the modified Nambu-Goto action. Appendix \ref{sec:polyakov-ng-relation} shows how the equations of motion extracted from the Nambu-Goto and Polyakov versions of the modified string action are equivalent to each other.

@@

In the decades prior to the advent of string theory a great deal of effort was put into attempting to quantize gravity via both the Lagrangian and Hamiltonian approaches. The Hamiltonian approach involves, as stated earlier, a choice of the foliation of the background geometry into a collection of spacelike surfaces $\Sigma_t$. Central to this approach was the ADM (Arnowitt-Deser-Misner) formalism which allows one to construct a Hamiltonian $H_{GR}$ for general relativity starting from the Einstein-Hilbert action $S_{EH}$. The resulting phase space is coordinatized by a configuration variable which is the 3-metric $h_{ab}$ of the ``leaves'' $\Sigma_t$ of the foliation and a momentum variable which is a function of the extrinsic curvature $k_{ab}$ of the leaves\footnote{Our notational convention is the following. Lowercase Greek letters from the middle of the alphabet $\mu, \nu, \ldots$ are spacetime indices which run from $(0 \ldots 3)$, whereas lowercase Roman letters $a,b,\ldots$ are spatial indices for quantities which live solely on the surfaces $\Sigma_t$ and take values in $(1,2,3)$}. The gravity Hamiltonian turns out to be a sum of two constraints known as the diffeomorphism (or ``momentum'') constraint $H_{diff}$ and the Hamiltonian constraint $H_{ham}$:
\begin{equation}
	H_{GR} = H_{diff} + H_{ham},
\end{equation}
and these are, in turn, functionals on the phase space of general relativity written in terms of $h_{ab}$ and $k_{ab}$. The idea then is that physical states of the theory $\ket{\Psi_{phys}} $, which can be written as functionals $\Psi[h_{ab}]$ of the 3-metric $h_{ab}$, must be annihilated by these constraints:
\begin{equation}
	H_{GR} \ket{\Psi_{phys}} \equiv 0
\end{equation}
While this procedure is straightforward in principle, in practice it was impossible to implement in the quantum theory due to the highly complicated non-polynomial dependence of the diffeomorphism and Hamiltonian constraints on the configuration and momentum variables. This unfortunate state of affairs persisted until the late 1980s when Abhay Ashtekar \cite{Ashketar1986New,Ashtekar1987New} recast general relativity as a BF theory of a dualised $\mathfrak{sl} (2, \C)$ connection (which becomes the self-dual part of said connection in the case of $\beta = i$)
\begin{equation} \label{eqn:self-dual-spin-connection}
	A_{\mu} ^{I J} = \omega ^{I J} _{\mu} - \frac{\beta}{2} \varepsilon ^{I J} _{\ \ K L} \omega ^{K L} _{\mu}
\end{equation}
and its conjugate momenta
\begin{equation} \label{eqn:densitized-tetrad}
	B^{I J} _{\mu \nu} = \left( \delta ^{I} _{K} \delta ^{J} _{L} + \frac{1}{2 \beta} \varepsilon ^{I J} _{\ \ K L} \right) e^{K} _{[ \mu} e^{L} _{\nu ]},
\end{equation}
which when restricted to a 3-dimensional hypersurface where $* (e \wedge e) = 0$ reduces to
\begin{equation} \label{eqn:Ashtekar-connection-canonical}
	A^{i} _{a} = \omega ^{i} _{a} + \beta K^{i} _{a}
\end{equation}
\begin{equation} \label{eqn:Ashtekar-E-field-canonical}
	E^{a} _{i} = \sqrt{q} e^{a} _{i} = \frac{1}{2} \varepsilon ^{a b c} \varepsilon _{i j k} e^{j} _{b} e^{k} _{c},
\end{equation}
with $K^{i} _{a}$ being the triad version of the extrinsic curvature $K_{a b} = \frac{1}{2} \mathcal{L}_{n} q_{a b}$ and $q$ the 3-metric. Ashtekar realized that the constraints of general relativity, when expressed in terms of these ``new variables'', simplified drastically and became polynomial functions of the tetrad and connection variables. It was quickly realized by various researchers that the resulting theory could be quantized using the same methods used to quantize Yang-Mills gauge theory \cite{Ashtekar1992Weaving,Ashtekar2004Background} and that the diffeomorphism constraint could be solved exactly in terms of so-called \emph{spin-network} states \cite{Rovelli1988Knot,Rovelli1990Loop,Ashtekar1992Gravitons}.

Following this, work by Rovelli and Smolin \cite{Rovelli1993Area,Rovelli1994Discreteness} demonstrated a remarkable feature of this theory, which came to be known as ``Loop Quantum Gravity'', was that one could construct quantum operators for geometric quantities such as areas of two-dimensional surfaces and volumes of three-dimensional regions. Moreover, these operators could be diagonalized exactly in the spin-network basis and a discrete spectrum for quantum of area and quantum of volume could be derived. This was the first time that physicists had discovered the ``atoms of space'' or the ``quanta of geometry'' in the true sense of the expression, in a theory of quantum gravity. One of the early triumphs of this formalism, which has unfortunately not received enough attention over the years by the larger high-energy theory community, was the calculation of the entropy of a Schwarzschild black hole \cite{Rovelli1996Black} in a fully quantum mechanical framework and showing that it matched the expected expression $S \sim A/4$ for the Bekenstein-Hawking entropy.

One key feature of the discreteness of spacetime itself is that the Ashtekar connection $A^{i} _{a}$ \footnote{Here, the index convention followed is that lowercase $i, j, k$ refer to 3-dimensional flat internal ($\mf{su}(2)$) indices and lowercase $a, b, c$ refer to 3-dimensional curved spacetime indices} can no longer be a continuous function of spacetime, rather it becomes a \emph{distribution}, assuming a constant value on one patch of space, then another value at another patch, etc \cite{Bodendorfer-LQG,Rovelli2015Covariant}. The consequence of this non-continuous distributional nature of the connection is that the triad (or Ashtekar electric field) operator, which formally would be
\begin{equation} \label{eqn:triad-operator}
	\Hat{\widetilde{E}}{}^{a} _{i} = - 8 \pi i \hbar G \frac{\delta}{\delta A^{i} _{a}}
\end{equation}
becomes ill-defined since $A^{i} _{a}$ is non-continuous (in particular, at the edges of a polyhedra it changes abruptly), so the triad needs to be \emph{smeared} over a surface where $A^{i} _{a}$ is constant
\begin{equation} \label{eqn:triad-flux-operator}
	\Hat{E}_{i} (S) = - 8 \pi i \hbar G \int _{S} \diff S_{a}  \frac{\delta}{\delta A^{i} _{a}},
\end{equation}
where $\diff S_{a} = \diff \sigma ^{b} \wedge \diff \sigma ^{c} \varepsilon _{a b c}$. This naturally leads to the \emph{area operator} of said surface
\begin{equation} \label{eqn:area-operator}
	\Hat{A} (S) = - 8 \pi i l_{pl} ^2 \beta \int _{S} \sqrt{\diff S_{a} \diff S_{b} \frac{\delta}{\delta A^{i} _{a}} \frac{\delta}{\delta A_{b i}}} .
\end{equation}
Notably, since $A^{i} _{a}$ is a $\mf{su}(2)$-valued connection, in the basis which diagonalises the area operator (the \emph{spin network} basis \cite{Bodendorfer-LQG}) $\ket{\Tr (h^{(j)} _{c} (A))}$, the eigenvalues of the area operator are just proportional to \emph{angular momentum} eigenvalues
\begin{equation} \label{eqn:area-eigenvalues}
	\Hat{A} \ket{\Tr (h^{(j)} _{c} (A))} = 8 \pi l_{pl} ^2 \beta \sqrt{j (j + 1)} \ket{\Tr (h^{(j)} _{c} (A))},
\end{equation}
with $j$ being the representation label of $\mf{su}(2)$ along the spin network edge piercing the surface under consideration. Thus, spin network edges carry angular momenta.

@@

Here, $k = l_{pl} / l_s$, where $l_{pl}$ is the Planck scale, the scale at which quantum geometric effects become important; $l_s$ is the string scale where quantum geometric effects due to area quantization become small; for the time being we take $\Delta$ to be a scalar constant which corresponds to the minimum quantum of area at the Planck scale\footnote{We will see later that $\Delta$ is, in fact, a scalar density of weight 2 which can be taken to be the determinant of an antisymmetric worldsheet tensor $\Delta _{a b} (x)$ and corresponds to the square of the quantum of area at the point $x$ where the edges of the bulk spin network state pierce the WS and endow it with quanta of area as described in the previous section.}. In the limit that $l_s \gg l_{pl}$, $k \ll 1$ and the string action reduces to the conventional Nambu-Goto action with small corrections coming from quantum geometry. In this limit we can expand the integrand as follows:
\begin{equation} \label{eqn:inverse-metric-correction}
	\sqrt{- (h + k \Delta)} \sim \sqrt{- h}\left(1 - \frac{1}{2} \frac{k \Delta}{(- h)} + \mc{O}(k^2/h^2)\right).
\end{equation}
If we take $k$ to be an expansion parameter, then it follows that it should also be small. The physical justification for this is the following picture. The microscopic picture of geometry at the Planck scale, which we adopt as the ``correct'' picture, is that given by loop quantum gravity in terms of spin networks and spin foams. The worldsheet picture emerges when one considers a large enough section of the spin network with a sufficiently large number of punctures. In this limit, the spin network can be approximated by a smooth geometry, and the worldsheet picture emerges as a low-energy effective description of the spin network. When $k \sim 1$, the discrete structure of the underlying spin network becomes manifest and the smooth worldsheet approximation is no longer valid, indicating that a full quantum gravitational treatment - \ie~ where geometry itself is fully quantum - is required.

@@

The action eq \eqref{eqn:modified-ng-action} has manifest background Poincaré invariance since just like the regular Nambu-Goto action since all its terms are derivatives of $X^{\mu}$ with all Lorentz indices contracted, thus are Lorentz scalars. At first glance it might seem to not be WS reparameterization invariant because of the second term, however, this is corrected by the fact that $\Delta$ is a scalar \emph{density} of weight 2, thus counteracting the inverse metric determinant. Moreover, if we look at that expression we see that it can be written as:
\begin{equation} \label{eqn:modified-ng-action-v2}
	S'_{NG}[h_{ab}] = -T \int \diff ^2 x \left( \sqrt{- h} - \frac{1}{2} {k \Delta}{\sqrt{- (h^{-1})}} \right),
\end{equation}
where $h^{-1}$ is now the determinant of the \emph{inverse} metric $h^{ab}$. As such, in the expression \eqref{eqn:modified-ng-action} we can see a duality between the first and second terms. If we replace the metric $h_{ab}$ by its inverse $h'_{ab} \equiv h^{ab}$, then the action in terms of $h'_{ab}$ is the same as \eqref{eqn:modified-ng-action}, but with the difference that the factor of $k \Delta / 2$ is mapped to $2 / (k \Delta)$:
\begin{align} \label{eqn:modified-ng-action-v3}
	S'_{NG}[h'_{ab}] & = -T' \int \diff ^2 x' \left( \sqrt{- h'} - \frac{2}{k \Delta} \sqrt{- (h')^{-1}} \right) \nonumber \\
	                 & = -T' \int \diff ^2 x' \left( \sqrt{- h'} - \onehalf {k' \Delta'}\sqrt{- (h')^{-1}} \right),
\end{align}
which has the same form as the original action \eqref{eqn:modified-ng-action}, as long as we make the replacements
\begin{subequations}
	\begin{equation} \label{eqn:T'}
		T \rightarrow T' = - \frac{1}{2} k T
	\end{equation}
	\begin{equation} \label{eqn:k-Delta}
		\frac{1}{2} {k \Delta} \rarrow \frac{1}{2} {k' \Delta'} = \frac{2} {k \Delta}
	\end{equation}
	\begin{equation} \label{eqn:d2x}
		\diff ^2 x \rightarrow \diff ^2 x' = \Delta \diff ^2 x
	\end{equation}
\end{subequations}
(or equivalently $\diff x^{a} \rightarrow \diff x' _{a} = \Delta _{a b} \diff x^{b}$). This is a duality between the physics at the Planck scale and the physics at the string scale, \ie~ between strong coupling ($k' \gg 1$) and weak coupling ($k \ll 1$), small worldsheet areas $h_{ab}$ and large worldsheet areas $h'_{ab}$ and between large string tension $T$ and small string tension $T'$.
